Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-27 article.tex
Bookmark after fixing Appendix

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \Laplacian^T\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.  A
close-form expression of our Jacobian and its detailed derivation is
given in \cref{sec:gradient-derivation}.

@@

Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
    i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
differentiation. Let $\vect{n}$ be a vector of length $q$. Let
$\vect{g}(\vect{n})$ be a vector function: it outputs a vector of
length $r$. Let $\mat{B}$ be a $q \times r$ matrix and
\begin{align}
  \vect{g}(\vect{n}) = \exp^{-\transpose{\mat{B}}\vect{n}}.
  \label{eq:example1}
\end{align}
In \cref{eq:example1}, the exponential is element-wise (not raising an
operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{g}}{\vect{n}} &= - \mat{B} \,
  \OpDiag{\exp^{-\transpose{\mat{B}}\vect{n}}}
\end{align}
Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp^{-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
      {\bm D}_c {\bm n})}}
\end{align}
In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
known and constant.

To calculate the derivative of the Hadamard product in \cref{eq:bigIA}
we first note the following: Let $\vect{u}(\vect{n})$ be a vector
function that outputs a vector of length $r$. Let $\mat{B}$ be a $r
\times q$ matrix. Then,
\begin{align}
  \label{eq:partial1}
  \PartDeriv{\transpose{\mat{B}} (\vect{g} \odot \vect{u})}{\vect{n}}
  = \left[ \PartDeriv{\vect{g}}{\vect{n}} \OpDiag{\vect{u}} +
    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{g}} \right] \mat{B}.
\end{align}
Then,
\begin{align}
  \label{eq:partial3}
  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}}{\vect{n}}
  =
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
\end{align}

Based on \cref{eq:partial4,eq:partial1,eq:partial3} we can derive a
close-form expression for the Jacobian of \cref{eq:bigIA}:
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}({\bm A}-{\bm B}){\bm C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  {\bm A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  {\bm B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  {\bm C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}

>>>>

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \cdot \eta \cdot
  \transpose{\Laplacian}\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the density at voxel $k$, i.e.,
$\partial i_c({\bm \Theta})/\partial{n^{\rm aerosol}(k)}$.  A
close-form expression of our Jacobian and its detailed derivation is
given in \cref{sec:gradient-derivation}.

@@

Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
    i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results relating to
differentiation. Let $\vect{n}$ be a vector of length $m$. Let
$\vect{a}(\vect{n})$ be a vector function: it outputs a vector of
length $r$. Let $\mat{C}$ be a $m \times r$ matrix and
\begin{align}
  \vect{a}(\vect{n}) = \exp[-\transpose{\mat{C}}\vect{n}].
  \label{eq:example1}
\end{align}
In \cref{eq:example1}, the exponential is element-wise (not raising an
operator to some power). Then
\begin{align}
  \label{eq:partial2}
  \PartDeriv{\vect{a}}{\vect{n}} &= - \mat{C} \,
  \OpDiag{\exp[-\transpose{\mat{C}}\vect{n}]}
\end{align}
Here we denote by $\OpDiag{\vect{v}}$ conversion of vector $\vect{v}$
into a diagonal matrix, whose main diagonal elements correspond to the
elements of $\vect{v}$. Using \cref{eq:partial2} we can calculate
\begin{align}
  \label{eq:partial4}
  \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
  {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
  \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}{\bm D}_c {\bm n})]}
\end{align}
In \cref{eq:partial4} we assume that $\vect{\tau}_c^{\rm air}$ is
known and constant.

To calculate the derivative of the Hadamard product in \cref{eq:bigIA}
we first note the following: Let $\vect{u}(\vect{n})$ be a vector
function that outputs a vector of length $r$. Let $\mat{C}$ be a $r
\times m$ matrix. Then,
\begin{align}
  \label{eq:partial1}
  \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot \vect{u})}{\vect{n}}
  = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
    \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right] \mat{C}.
\end{align}
Then,
\begin{align}
  \label{eq:partial3}
  \PartDeriv{\, \varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}}{\vect{n}}
  =
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
  \nonumber \\
  \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
      aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}
  \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
\end{align}

Based on \cref{eq:partial4,eq:partial1,eq:partial3} we can derive a
close-form expression for the Jacobian of \cref{eq:bigIA},
\begin{align}
  {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
  ,
  \label{eq:gradient2}
\end{align}
where
\begin{align}
  \label{eq:gradient3}
  \abbrev{A} &= \varpi^{\rm aerosol}\sigma^{\rm aerosol}
  \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
  \abbrev{B} &= {\sigma}^{\rm aerosol}\transpose{{\bm D}_c} \nonumber\\
  & \;\;\; \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
      scatter}_c) \odot{\bm n}
    ]} \nonumber \\
  \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
      aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
\end{align}
